---
title: "Evaluating Statistical Models for Predicting Next-Season Wins Above Replacement"
author: "Group 3"
date: "2025-12-05"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```
 
```{r}
library(knitr)
library(ggplot2)
```
 
 
##Introduction
 
##Background and Motivation
 Wins Above Placement (WAR) is one of the most widely used metrics in modern baseball analytics. It estimates the total number of wins a player contributes to their team compared to a player who could be readily called up from the minor league, or signed for a low cost. Since WAR combines many aspects of performance: hitting, defense, positional value, and baserunning, it is viewed as a comprehensive measure of a player's overall value.
 
 
##Purpose
 
##Data Cleaning
 
 
 ....
 
 
##Methods
 
##OLS
 
 The Ordinary Least Squares ...explain the method...
 
Our OLS model outputs an $R^2$ value of 0.8219. Meaning that it explains about 82% of the variation in WAR using batting statistics. 

It also outputted a Residual Standard Error of 0.73, confirming the model's predictions are consistently within about 0.7-0.8 WAR of the true value



##LASSO
 
 Least Absolute Shrinkage and Selection Operator... explain
 
 Our LASSO model performs both regulariztion and feature selction of the data 
 #BOOSTING


##GRAPHS
 
##OLS Scatterplot
 
##LASSO Scatterplot
 
##BOOSTING Scatterplot
 
 
##Comparison BAR graphs


 

 
##CONCLUSION