---
title: "Presentation"
output:
  powerpoint_presentation: default
  beamer_presentation: default
date: "2025-12-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r echo=FALSE}
library(ggplot2)
library(Metrics)
lasso_rmse_train <- rmse(lasso_preds_train, truth = WAR, estimate = .pred)$.estimate
lasso_mae_train <- mae(lasso_preds_train, truth = WAR, estimate = .pred)$.estimate

lasso_rmse_test <- rmse(lasso_preds_test, truth = WAR, estimate = .pred)$.estimate
lasso_mae_test <- mae(lasso_preds_test, truth = WAR, estimate = .pred)$.estimate
lasso_metrics <- data.frame(train_rmse = lasso_rmse_train ,test_rmse = lasso_rmse, 
                            train_mae = lasso_mae_train, test_mae = lasso_mae_test, 
                            non_zero = non_zero, shrunk_coefs = zero) 

lasso_metrics|>
  ggplot() +
  geom_bar(aes(x = test_rmse)) +
  theme_bw()
```

## Predicting WAR 